---
title: "Store Service-Channel Modality & Experience Outcomes"
author: "Jensen Hu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile,
                    encoding = encoding,
                    output_dir  = here::here("output"),
                    output_file = "store-modality-analysis.html")})
output:
  html_document:
    toc: true
---

**Disclaimer:** This notebook is a synthetic, portfolio demonstration. All
organizations, identifiers, and data below are fictional or randomly
generated. It does not represent any real employer, client, or dataset, and
none of the numbers should be treated as meaningful.

It demonstrates a handful of techniques from applied survey/administrative
data analysis: imputing a low-response rater group from a higher-response
one, reshaping a long panel into a wide one keyed on two comparison periods,
a checked join that surfaces unmatched keys, and looping a robust-SE
regression across many outcomes at both the unit level and a group-aggregated
level, with results written out to a multi-sheet workbook.

```{r setup, message = FALSE}
### Setup ---------------------------------------------------------------------#
rm(list = ls())
set.seed(20240115)

options(dplyr.print_max = 100)

library(dplyr)
library(tidyr)
library(purrr)
library(glue)
library(haven)
library(assertr)
library(estimatr)
library(openxlsx)
library(knitr)
library(here)

data_dir <- here("data")
out_dir  <- here("output")

source(here("R", "generate_synthetic_data.R"))
source(here("R", "utils.R"))
```

## Read in Analytic File

```{r}
synthetic <- generate_store_panel()
df       <- synthetic$store_panel
survey_completion <- synthetic$survey_completion
```

## Clean data

```{r}
vars <- c(
  "store_id",
  "store_name",
  "region_id",
  "region_name",
  "resp_cust_survey",
  "resp_emp_survey",
  "svc_instore_prop",
  "svc_curbside_prop",
  "svc_delivery_prop",
  "fiscal_year",
  "market_type",
  "store_size_tier",
  "total_customers",
  "pct_seg_young_adult",
  "pct_seg_family",
  "pct_seg_senior",
  "pct_seg_business",
  "pct_seg_student",
  "pct_seg_other",
  "discount_zone_flag",
  "emp_fte",
  "emp_customer_ratio",
  "total_customers_loyalty",
  "numvalid_ops",
  "numvalid_svc",
  "pct_target_ops",
  "pct_target_svc",
  "idx_overall_cust",
  "idx_loyalty_cust",
  "idx_service_cust",
  "idx_culture_cust",
  "idx_overall_emp",
  "idx_loyalty_emp",
  "idx_service_emp",
  "idx_culture_emp",
  "idx_overall_mgr",
  "idx_loyalty_mgr",
  "idx_service_mgr",
  "idx_culture_mgr",
  "include_analysis"
)

df$fiscal_year <- haven::zap_label(df$fiscal_year)

list_index <-
  list(
    c("idx_overall_mgr", "idx_overall_emp"),
    c("idx_loyalty_mgr", "idx_loyalty_emp"),
    c("idx_service_mgr", "idx_service_emp"),
    c("idx_culture_mgr", "idx_culture_emp")
  )

# impute manager-reported score with the employee score when missing
for (pair in list_index) {

  print(pair)

  x <- pair[1]
  y <- pair[2]

  print(paste("number missing before = ", length(df[[x]][is.na(df[[x]])])))

  df[[x]][is.na(df[[x]])] <- df[[y]][is.na(df[[x]])]
  assign("df_imputed", df)

  print(paste("number missing after = ", length(df[[x]][is.na(df[[x]])])))
}


store_wide <- df_imputed %>%
  # restrict to stores eligible for this analysis
  filter(include_analysis == 1) %>%
  mutate(
    fiscal_year = factor(fiscal_year, ordered = TRUE,
                          levels = c("1", "2", "3", "4", "5", "6")),
    region_id = substring(store_id, 1, 4)
  ) %>%
  # nonmissing service-channel data
  filter(
    !is.na(svc_instore_prop) |
      !is.na(svc_curbside_prop) |
      !is.na(svc_delivery_prop)
  ) %>%
  # restrict to baseline (FY19) and follow-up (FY22) periods
  filter(fiscal_year %in% c(3, 6)) %>%
  mutate(
    fiscal_year = case_when(
      fiscal_year == 3 ~ "fy19",
      fiscal_year == 6 ~ "fy22"
    )
  ) %>%
  select(all_of(vars)) %>%
  pivot_wider(
    id_cols = vars[1:9],
    names_from = fiscal_year,
    values_from = vars[11:length(vars)]
  )

# switch between employee (1) vs manager (0) score version
toggle_role <- 1


saveRDS(store_wide, file.path(data_dir, "store_modality_wide.rds"))

knitr::kable(head(store_wide))
```


## Count of Stores w/ Survey Response

```{r}

store_wide %>%
  filter(resp_emp_survey == 1 | resp_cust_survey == 1) %>%
  checked_join(
    survey_completion,
    by = c("region_id" = "csat_region_key"),
    tab = TRUE
  ) %>%
  mutate(resp_cust_survey = as.character(resp_cust_survey),
         resp_emp_survey  = as.character(resp_emp_survey)) %>%
  group_by(merge, resp_cust_survey, resp_emp_survey) %>%
  tally()

```


## Table: Service-Channel Mix
### Service-Channel Mix - Employee-surveyed stores
```{r}
# analysis
analysis <- store_wide %>%
  mutate(
    # market-type construct
    urban_fy19    = as.numeric(market_type_fy19 == 1),
    suburban_fy19 = as.numeric(market_type_fy19 == 2),
    town_fy19     = as.numeric(market_type_fy19 == 3),
    rural_fy19    = as.numeric(market_type_fy19 == 4)
  )

# subset data
employee_data <- analysis %>% filter(resp_emp_survey == 1)
customer_data <- analysis %>% filter(resp_cust_survey == 1)

# Table: Service-Channel Mix
modality_emp <-
  employee_data %>%
  select(
    store_id,
    svc_curbside_prop,
    svc_instore_prop,
    svc_delivery_prop
  ) %>%
  arrange(desc(svc_curbside_prop)) %>%
  verify(abs(svc_curbside_prop + svc_instore_prop + svc_delivery_prop - 100) < 1e-6) %>%
  mutate_if(is.numeric, ~round(.x, 2)) %>%
  rename(
    "Store ID"     = store_id,
    "% Curbside"   = svc_curbside_prop,
    "% In-Store"   = svc_instore_prop,
    "% Delivery"   = svc_delivery_prop
  )
knitr::kable(modality_emp)
```

### Service-Channel Mix - Customer-surveyed stores
```{r}
modality_cust <-
  customer_data %>%
  select(
    store_id,
    svc_curbside_prop,
    svc_instore_prop,
    svc_delivery_prop
  ) %>%
  arrange(desc(svc_curbside_prop)) %>%
  verify(abs(svc_curbside_prop + svc_instore_prop + svc_delivery_prop - 100) < 1e-6) %>%
  mutate_if(is.numeric, ~round(.x, 2)) %>%
  rename(
    "Store ID"     = store_id,
    "% Curbside"   = svc_curbside_prop,
    "% In-Store"   = svc_instore_prop,
    "% Delivery"   = svc_delivery_prop
  )
knitr::kable(modality_cust)
```


## Regression
```{r}

if (toggle_role == 1) {
  # employee - version
  dv <- c(
    "idx_overall_cust_fy22",
    "idx_loyalty_cust_fy22",
    "idx_service_cust_fy22",
    "idx_culture_cust_fy22",
    "idx_overall_emp_fy22",
    "idx_loyalty_emp_fy22",
    "idx_service_emp_fy22",
    "idx_culture_emp_fy22"
  )

  sc_fy19 <- c(
    "idx_overall_cust_fy19",
    "idx_loyalty_cust_fy19",
    "idx_service_cust_fy19",
    "idx_culture_cust_fy19",
    "idx_overall_emp_fy19",
    "idx_loyalty_emp_fy19",
    "idx_service_emp_fy19",
    "idx_culture_emp_fy19"
  )
} else {
  # manager - version
  dv <- c(
    "idx_overall_cust_fy22",
    "idx_loyalty_cust_fy22",
    "idx_service_cust_fy22",
    "idx_culture_cust_fy22",
    "idx_overall_mgr_fy22",
    "idx_loyalty_mgr_fy22",
    "idx_service_mgr_fy22",
    "idx_culture_mgr_fy22"
  )

  sc_fy19 <- c(
    "idx_overall_cust_fy19",
    "idx_loyalty_cust_fy19",
    "idx_service_cust_fy19",
    "idx_culture_cust_fy19",
    "idx_overall_mgr_fy19",
    "idx_loyalty_mgr_fy19",
    "idx_service_mgr_fy19",
    "idx_culture_mgr_fy19"
  )
}


svc_list <- c(
  "svc_curbside_prop",
  "svc_delivery_prop",
  "svc_instore_prop",
  "svc_curbside_prop + svc_delivery_prop"
)

regression <- function(x, y, z) {

  if (x %in% c(1, 2, 3, 4)) {
    print(paste(dv[x], "~", svc_list[y], "+", sc_fy19[x]))
    fit <- estimatr::lm_robust(as.formula(paste(dv[x], "~", svc_list[y], "+", sc_fy19[x])), data = customer_data)
  } else {
    print(paste(dv[x], "~", svc_list[y], "+", sc_fy19[x]))
    fit <- estimatr::lm_robust(as.formula(paste(dv[x], "~", svc_list[y], "+", sc_fy19[x])), data = employee_data)
  }
  print(summary(fit))

  out <- data.frame(
    "dv"          = dv[x],
    "Coefficient" = fit$coefficients[z],
    "SE"          = fit$std.error[z],
    "p-value"     = fit$p.value[z],
    "CI Lower"    = fit$conf.low[z],
    "CI Upper"    = fit$conf.high[z]
  )

  out$svc_var <- row.names(out)
  out$"p<.05" <- ifelse(out$p.value < .05, "*", "")

  out <- out %>%
    mutate(across(Coefficient:CI.Upper, ~round(.x, 2))) %>%
    relocate(svc_var, .before = dv)

  return(out)
}

regression_agg <- function(x, y, svc_var) {

  # prepare data
  data <-
    (if (x %in% c(1, 2, 3, 4)) {
      customer_data
    } else {
      employee_data
    }) %>%
    # mean of scores by region_id
    group_by(region_id) %>%
    mutate(
      "{dv[x]}_agg"      := mean(.data[[glue("{dv[x]}")]], na.rm = TRUE),
      "{sc_fy19[x]}_agg" := mean(.data[[glue("{sc_fy19[x]}")]], na.rm = TRUE)
    ) %>%
    select(
      region_id,
      glue("{dv[x]}_agg"),
      glue("{sc_fy19[x]}_agg"),
      all_of(svc_var)
    ) %>%
    # distinct by region_id
    unique()

  # run regression
  print(paste(glue("{dv[x]}_agg"), "~", svc_list[y], "+", glue("{sc_fy19[x]}_agg")))
  fit <- estimatr::lm_robust(as.formula(paste(glue("{dv[x]}_agg"), "~", svc_list[y], "+", glue("{sc_fy19[x]}_agg"))), data = data)

  print(summary(fit))

  # structure output
  out <- data.frame(
    "dv"          = rep(glue("{dv[x]}_agg"), length(svc_var)),
    "Coefficient" = fit$coefficients[svc_var],
    "SE"          = fit$std.error[svc_var],
    "p-value"     = fit$p.value[svc_var],
    "CI Lower"    = fit$conf.low[svc_var],
    "CI Upper"    = fit$conf.high[svc_var]
  )
  out$svc <- row.names(out)
  out$"p<.05" <- ifelse(out$p.value < .05, "*", "")
  out <- out %>%
    mutate(across(Coefficient:CI.Upper, ~round(.x, 2))) %>%
    relocate(svc, .before = dv)

  return(out)
}

```

### Model 1: svc_curbside_prop
```{r}
model1 <- map_dfr(c(1:length(dv)), function(x) regression(x, y = 1, z = "svc_curbside_prop"))
knitr::kable(model1)
```

### Model 1: svc_curbside_prop - region level
```{r}
model1_agg <- map_dfr(c(1:length(dv)), function(x) regression_agg(x, y = 1, svc_var = "svc_curbside_prop"))
knitr::kable(model1_agg)
```

### Model 2: svc_delivery_prop
```{r}
model2 <- map_dfr(c(1:length(dv)), function(x) regression(x, y = 2, z = "svc_delivery_prop"))
knitr::kable(model2)
```

### Model 2: svc_delivery_prop - region level
```{r}
model2_agg <- map_dfr(c(1:length(dv)), function(x) regression_agg(x, y = 2, svc_var = "svc_delivery_prop"))
knitr::kable(model2_agg)
```

### Model 3: svc_instore_prop
```{r}
model3 <- map_dfr(c(1:length(dv)), function(x) regression(x, y = 3, z = "svc_instore_prop"))
knitr::kable(model3)
```

### Model 3: svc_instore_prop - region level
```{r}
model3_agg <- map_dfr(c(1:length(dv)), function(x) regression_agg(x, y = 3, svc_var = "svc_instore_prop"))
knitr::kable(model3_agg)
```

### Model 4: svc_curbside_prop + svc_delivery_prop
```{r}
model4 <- map_dfr(c(1:length(dv)), function(x) regression(x, y = 4, z = 2:3)) %>% arrange(svc_var)
knitr::kable(model4)
```

### Model 4: svc_curbside_prop + svc_delivery_prop - region level
```{r}
model4_agg <- map_dfr(c(1:length(dv)), function(x) regression_agg(x, y = 4, svc_var = c("svc_curbside_prop", "svc_delivery_prop"))) %>% arrange(svc)
knitr::kable(model4_agg)
```


## Output
```{r, eval = TRUE}

# output ####
wb <- createWorkbook()

addWorksheet(wb, "Modality EMP")
freezePane(  wb, "Modality EMP", firstRow = TRUE)
writeData(   wb, "Modality EMP",  modality_emp, headerStyle = createStyle(textDecoration = "bold"))
addWorksheet(wb, "Modality CUST")
writeData(   wb, "Modality CUST",  modality_cust, headerStyle = createStyle(textDecoration = "bold"))

addWorksheet(wb, "Model1")
writeData(   wb, "Model1",  model1, headerStyle = createStyle(textDecoration = "bold"))
addWorksheet(wb, "Model1 region level")
writeData(   wb, "Model1 region level",  model1_agg, headerStyle = createStyle(textDecoration = "bold"))
addWorksheet(wb, "Model2")
writeData(   wb, "Model2",  model2, headerStyle = createStyle(textDecoration = "bold"))
addWorksheet(wb, "Model2 region level")
writeData(   wb, "Model2 region level",  model2_agg, headerStyle = createStyle(textDecoration = "bold"))
addWorksheet(wb, "Model3")
writeData(   wb, "Model3",  model3, headerStyle = createStyle(textDecoration = "bold"))
addWorksheet(wb, "Model3 region level")
writeData(   wb, "Model3 region level",  model3_agg, headerStyle = createStyle(textDecoration = "bold"))
addWorksheet(wb, "Model4")
writeData(   wb, "Model4",  model4, headerStyle = createStyle(textDecoration = "bold"))
addWorksheet(wb, "Model4 region level")
writeData(   wb, "Model4 region level",  model4_agg, headerStyle = createStyle(textDecoration = "bold"))

saveWorkbook(wb, file.path(out_dir, "store-svc-modality-results.xlsx"), overwrite = TRUE)

```
